### 2017-12-13 README.Rmd
update readme to use devtools again

```{r gh-installation, eval = FALSE}
install.packages("remotes")
options(repos = c("https://cran.rstudio.com/", "http://bioconductor.org/packages/release/bioc/", "http://bioconductor.org/packages/release/data/annotation", "http://bioconductor.org/packages/release/data/experiment", "http://bioconductor.org/packages/release/extra"))
remotes::install_github("Zouter/dynalysis", dependencies = TRUE)
```

>>>>

```{r gh-installation, eval = FALSE}
install.packages("devtools")
setRepositories(ind = 1:2)
devtools::install_github("Zouter/dynalysis", dependencies = T, upgrade = T)
```
